---
title: "Covid-19 Report"
author: "Arturo Prieto Tirado"
date: "09/03/2021"
output: pdf_document
params:
  selected_date: input$selected_date
  selected_location: input$selected_location
---
```{r include=FALSE}
vaccines = read_csv(url("https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv")) %>% drop_na() 
#delete ISO code
vaccines=vaccines[c(-2,-7,-8,-10)]
  library(tidyverse)
  vaccines_date <- vaccines %>% 
    mutate_at(c("date", "location"), as.factor) %>%
    filter(date %in% params$selected_date, location %in% params$selected_location)
```

# Countries

The countries you selected were:

```{r, echo=FALSE}
# The `params` object is available in the document.
params$selected_location
```

# Dates

The dates you selected were:

```{r, echo=FALSE}
# The `params` object is available in the document.
params$selected_date
```


# Total vaccinations for your selection

The following plot shows total vaccination for the countries and dates you selected (it can happen that a given country did not vaccinate on your selected date, thus, not appearing).

```{r echo=FALSE}
ggplot(vaccines_date, aes(x=location, y=total_vaccinations, fill=date)) + 
  geom_bar(stat="identity", position=position_dodge())